---
title: "Option Analysis Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("OptionAnalysis.R" )
library("knitr")
pricing.date=today
```

## Position Summary

The report is being run on `r format(today(),"%d-%b-%Y")` with a spot price of `r spot.price`.  

This report is being run on the following positions.

```{r positions, echo=FALSE}

  # Get position table
  pos <- read.positiondata( "string", "Expiration", "%d-%b-%y")

  # Merge in current prices, and closeout prices
  last.price <- mapply( process.closeout, pos$Closeout, pos$Type, pos$Strike, option.prices  )
    
  option.prices.df <- data.frame( ID = names(option.prices), LastPrice = last.price)
  pos <- merge(pos, option.prices.df, by = "ID")
  
  # Generate discount factors
  df.curve <- bootstrap.df.curve()
  pos$DiscountFactor <- discount.factor( df.curve, pos$Expiration )
  
  # Calculate implied volatilities
  ivol <- mapply( implied.volatility, pos$LastPrice, pos$Type, pos$Strike, pos$Expiration, spot.price, pos$DiscountFactor, pricing.date  )
  pos$Volatility <- ivol

  # Recover prices
  pos$LastPriceCalc <- mapply( BSPrice, pos$Type, pos$Strike, pos$Expiration, spot.price, pos$Volatility, pos$DiscountFactor, pricing.date )
  
  pos.display <- pos
  # Volatility in percent, rounded to decimals
  pos.display$Volatility <- round(pos.display$Volatility*1000)/10
  # Last price calc rounded to 1/10 pennies
  pos.display$LastPriceCalc <- round(pos.display$LastPriceCalc*1000)/1000
  pos.display$DiscountFactor <- NULL
  kable( pos.display )

  
  pos$NPV <- pos$LastPrice * lot.size * pos$Quantity
  pos$LTD.PNL <- pos$NPV - pos$CostBasis * lot.size * pos$Quantity

```


## Risk Sensivities

Portfolio risk sensitivities


```{r greeks calc, echo=FALSE}
  # Calculate per-unit greeks
  pos.open <- filter( pos, Closeout == 0)

  greeks.mapply <- mapply( BSGreeks, pos.open$Type, pos.open$Strike, pos.open$Expiration, spot.price, pos.open$Volatility, pos.open$DiscountFactor, pricing.date )
  greeks <- data.frame( ID = pos.open$ID )
  greeks <- cbind( greeks, df.convert( t(greeks.mapply)))
  
```


```{r risk measure calc, echo=FALSE}
  # Generate sensitivity risk reports for the portfolio
  risk.measure.spec <- data.frame(
    name = c( "delta", "delta 1%", "dv100", "vega 1%", "daily carry" ),
    greek = c( "delta", "delta", "rho", "vega", "tau" ),
    delta = c( 0.01, spot.price/100, 0.01, 0.01, 1/365 ),
    stringsAsFactors = FALSE
  )
  risk.report.df <- risk.report( pos.open, greeks, risk.measure.spec )
  totals <- apply( subset( risk.report.df, select=-ID ), MARGIN=2, sum)

  kable( totals, digits=2)
```

<p><p>
Risk sensitivities by position

```{r risk measures breakout, echo=FALSE}
  kable( risk.report.df, digits=2 )
```
  
## P&L Projection 

Profit and loss projection for various future dates and underlying spot price scenarios.

```{r pnl projection, echo=FALSE}  
  # Generate a pnl projection matrix
  spots <- spot.price * c( 0.5, 0.75, 0.9, 0.95, 1, 1.05, 1.1, 1.25 )
  spots <- spot.price * c( 0.5, 0.75, 0.9, 0.95, 1, 1.05, 1.1, 1.25 )
  spots <- sort( c( spots, 10, 12.5 ) )

  dates <- c( pricing.date + c(0,7), pricing.date %m+% months(c(1,3,6,12, 18), FALSE))
  pnl.report.df <- pnl.report( pos, spots, dates, df.curve )
  
  pnl.summary <- pnl.report.df %>% 
    group_by( spot, pricing.date ) %>%
    summarize( PNL=sum(PNL), LTD.PNL =sum(LTD.PNL), NPV=sum(NPV))
  
  kable( dcast( pnl.summary, pricing.date ~ spot, value.var="LTD.PNL"), digits=0, caption="Overall PNL" )
  kable( dcast( pnl.summary, pricing.date ~ spot, value.var="PNL"), digits=0, caption="PNL from present" )
  kable( dcast( pnl.summary, pricing.date ~ spot, value.var="NPV"), digits=0, caption="NPV" )
```

In graphical format

```{r pnl graph, echo=FALSE, fig.height=4, fig.width=6}

  scale.pref <- scale_y_continuous( labels = comma ) 
  
  ggplot( pnl.summary ) +geom_line( aes(x=pricing.date, y=PNL, color=as.character( spot ))) + scale.pref + scale_color_discrete( name = "spot") + labs(x="date", y="PNL")+ggtitle("PNL from present")
  ggplot( pnl.summary )  +geom_line( aes(x=spot, y=PNL, color=as.character(pricing.date)))+ scale.pref+ scale_color_discrete( name = "date")+ labs(x="spot", y="PNL")+ggtitle("PNL from present")

  ggplot( pnl.summary ) +geom_line( aes(x=pricing.date, y=LTD.PNL, color=as.character( spot )))+ scale.pref+ scale_color_discrete( name = "spot")+labs(x="date", y="PNL")+ ggtitle("Overall PNL")
  ggplot( pnl.summary )  +geom_line( aes(x=spot, y=LTD.PNL, color=as.character(pricing.date)))+ scale.pref+ scale_color_discrete( name = "date" )+labs(x="spot", y="PNL")+ ggtitle("Overall PNL")
```

## Option Greeks

Black-Scholes greeks for each position.

```{r greeks print, echo=FALSE}
  kable( greeks, digits=3)
```

## Interest Rates

Current interest rates, bootstrapped from ICE Libor and ICE Swaps.

```{r interest rates, echo=FALSE}
  # Generate an interst rate curve
  dates.plot = c( pricing.date+1,pricing.date %m+% months(1:15))
  df.plot = discount.factor( df.curve, dates.plot )
  rates.plot = -log( df.plot )/calc.term(dates.plot,pricing.date)*100
  qplot( dates.plot, rates.plot, geom="line", xlab="date", ylab="interest rate (%)")
```



